\bf A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-06-07 paper/paper-jsdse/paper-jsdse.tex
hgc confusion
unsatisfactory to disappointing

The highest grade completed has some confusion. There are several ways this is reported, including the highest grade ever completed and also the \texttt{hgc} at each survey year. To match the original data, it is appropriate to use the \texttt{hgc} while in high school. The documentation suggests this variable is available, but it is not actually present in the data. Hence, to match the original data, we have calculated the \texttt{hgc} to match the \texttt{hgc} achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match the original for a few individuals.

@@

Ultimately, the refreshed data is reasonably similar to the original but unsatisfactorily far from it. The last step required would be to inflation-adjust wages. This is better to do with each wave of new data added so that it is relative to the last date in the data. Our decision was to provide the raw wages and include code to make the adjustment as part of the package.

>>>>

The reporting of highest grade completed is confusing. There are several ways this is reported, including the highest grade ever completed and also the \texttt{hgc} at each survey year. To match the original data, it is appropriate to use the \texttt{hgc} while in high school. The documentation suggests this variable is available, but it is actually not. Hence, to match the original data, we have calculated the \texttt{hgc} to match the \texttt{hgc} achieved in the years between 1979 and 1994 based on the yearly survey value. The result does not exactly match the original for a few individuals.

@@

Ultimately, the refreshed data is reasonably similar to the original but disappointingly far from it. The last step required would be to inflation-adjust wages. This is better to do with each wave of new data added so that it is relative to the last date in the data. Our decision was to provide the raw wages and include code to make the adjustment as part of the package.
